NHF1 Tandem Deamination Data Generation

### 2022-06-13 R/GM12878TandemDeaminationDataGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

# Write the simplified mismatch data
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    fwrite(cisplatinMismatchData[[i]][[j]], sep = '\t', na = "NA",
           file = generateFilePath(
             tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
             repitition = names(cisplatinMismatchData)[i], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}
```

@@

for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    fwrite(cisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c(mismatchType)
    ))
  }
}
```

@@

for (i in seq_along(cisplatinGroupedStats)) {
  for (j in seq_along(cisplatinGroupedStats[[i]])) {
    fwrite(cisplatinGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
             strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}
```

@@

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

# Read mismatch frequency z-scores.
cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

@@

```{r generate_and_write_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = lapply(threePrimeMismatchAnchoredCisplatinData,
                                            tabulateNucFreqByPosTimepointAndLength)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  fwrite(threePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCisplatinNucFreq = lapply(fivePrimeMismatchAnchoredCisplatinData,
                                           tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fwrite(fivePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

```{r generate_and_write_sequence_frequencies}
threePrimeMMAnchoredCisplatinSeqFreq = lapply(
  threePrimeMismatchAnchoredCisplatinData,function(mismatchDataRep) {
    lapply(mismatchDataRep, function(mismatchData) {
      getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
    })
  }
)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fwrite(threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = lapply(
  fivePrimeMismatchAnchoredCisplatinData, function(mismatchDataRep) {
    lapply(mismatchDataRep, function(mismatchData) {
      getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
    })
  }
)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fwrite(fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

>>>>

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

# Write the simplified mismatch data
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    fwrite(cisplatinMismatchData[[i]][[j]], sep = '\t', na = "NA",
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
             repitition = names(cisplatinMismatchData)[i], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}
```

@@

for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    fwrite(cisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c(mismatchType)
    ))
  }
}
```

@@

for (i in seq_along(cisplatinGroupedStats)) {
  for (j in seq_along(cisplatinGroupedStats[[i]])) {
    fwrite(cisplatinGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
             strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering,
             includedMismatches = mismatchType
           ))
  }
}
```

@@

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

# Read mismatch frequency z-scores.
cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

@@

```{r generate_and_write_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = lapply(threePrimeMismatchAnchoredCisplatinData,
                                            tabulateNucFreqByPosTimepointAndLength)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  fwrite(threePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCisplatinNucFreq = lapply(fivePrimeMismatchAnchoredCisplatinData,
                                           tabulateNucFreqByPosTimepointAndLength, posType = FIVE_PRIME)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fwrite(fivePrimeMismatchCisplatinNucFreq[[i]], sep = '\t', file = generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

```{r generate_and_write_sequence_frequencies}
threePrimeMMAnchoredCisplatinSeqFreq = lapply(
  threePrimeMismatchAnchoredCisplatinData,function(mismatchDataRep) {
    lapply(mismatchDataRep, function(mismatchData) {
      getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("CG","CA","TG","TA"))
    })
  }
)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fwrite(threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = lapply(
  fivePrimeMismatchAnchoredCisplatinData, function(mismatchDataRep) {
    lapply(mismatchDataRep, function(mismatchData) {
      getSequenceFreqByReadLengthAndPos(mismatchData, querySequences = c("TGG"), posType = FIVE_PRIME)
    })
  }
)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fwrite(fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

### 2022-06-13 R/GM12878TandemDeaminationFigureGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMismatchData)) {
  for (j in seq_along(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_mismatch_frequency_z-score_tables}
cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_mismatch_position_statistics}
cisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                             rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(cisplatinGroupedStats)) {
  for (j in seq_along(cisplatinGroupedStats[[i]])) {
    cisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
      strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering,
      includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  threePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fivePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

@@

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints,
                                            rep2 = cisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints,
                                           rep2 = cisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

>>>>

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints,
                             rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMismatchData)) {
  for (j in seq_along(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_mismatch_frequency_z-score_tables}
cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints)
for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_mismatch_position_statistics}
cisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                             rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(cisplatinGroupedStats)) {
  for (j in seq_along(cisplatinGroupedStats[[i]])) {
    cisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
      strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering,
      includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCisplatinNucFreq)) {
  threePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCisplatinNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCisplatinNucFreq)) {
  fivePrimeMismatchCisplatinNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMismatchCisplatinNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

@@

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints,
                                            rep2 = cisplatinTimepoints)
for (i in seq_along(threePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    threePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(threePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCisplatinSeqFreq = list(rep1 = cisplatinTimepoints,
                                           rep2 = cisplatinTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])) {
    fivePrimeMMAnchoredCisplatinSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(fivePrimeMMAnchoredCisplatinSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCisplatinSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

### 2022-06-13 R/NHF1TandemDeaminationDataGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4-PP", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

>>>>

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```

@@

```{r read_expanded_mismatch_data}
# Get file paths for the expanded mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], expansionNum = expansionOffset, filtering = filtering,
      includedMismatches = mismatchType
      ))
  }
}
```
